data_collation

### 2024-04-12 scripts/data_collation.Rmd
updated site info data

@@

# remove columns with observer and unneeded data
UPC_data <- UPC_data[ -c(21:24) ]
```

@@

# use rbind.fill() method in R to combine data frames with different columns
site.info.dat <- rbind.fill(Site_info_2017, Site_info_2018, Site_info_template_v1)

>>>>

# Rename ft. weatherill to fort wetherill
kelp_data$SITE[kelp_data$SITE == "Ft Weatherill"] <- "Fort Wetherill"

@@

# Rename fort weatherill
UPC_data$SITE[UPC_data$SITE == "Fort Weatherill"] <- "Fort Wetherill"

# remove columns with observer and unneeded data
UPC_data <- UPC_data[ -c(21:24) ]

# Make all columns capitalized
colnames(UPC_data) <- toupper(colnames(UPC_data))

# Use lubridate to format date to be consistent
UPC_data$DATE <- mdy(UPC_data$DATE)

# output updated dataframe
write.csv(UPC_data, "output/cleaned_data/UPC.data.clean.csv", row.names = FALSE)

#UPC dataframe does not have month and day so that is why it isn't connecting fully
```

@@

# Make all columns capitalized
colnames(Site_info_2018) <- toupper(colnames(Site_info_2018))

# combine site collection data
site.info.dat <- rbind.fill(Site_info_2017, Site_info_2018, Site_info_template_v1)

# Austin - the site info for 2018 has a start and stop latitude so don't know what to do here
